
\documentclass[times,11pt]{letter}

%Top
\setlength{\headheight=0.0in}
\setlength{\headsep=0.0in}
\setlength{\voffset=-1in}
\setlength{\topmargin=2.5cm}

%Sides
\setlength{\hoffset}{-1.0in}
\setlength{\oddsidemargin}{2.25cm}

% Lengths
\setlength{\textwidth}{16.69cm}
\setlength{\textheight}{22.94cm}

\let\oldmarginpar\marginpar
%\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\small\sf #1]{\raggedright\small\sf #1}}
\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\small\sf]{\raggedright\small\sf }}

\usepackage{url}
\usepackage{xspace}

\begin{document}
\begin{center}
{\Large{\textsc{  Henri Casanova - C.V.}}}\\
~\\
University of Hawai`i at M\=anoa\\
Information and Computer Sciences Department\\
1680 East-West Road, POST 317, Honolulu, HI 96822, U.S.A.\\
Voice: +1 808 956-2649~~~~~~~~~Fax: +1 (808) 956-3548\\
\url{henric@hawaii.edu}~\\
\url{http://henricasanova.github.io/}~\\
\end{center}
~\\
\noindent
{\large{\bf EDUCATION}}

\begin{description}

\item []{\bf Ph.D.} -- Computer Science, University of Tennessee, Knoxville, Tennessee, U.S.A.,  {\bf 1998}
  \begin{itemize}
  \item[] Dissertation: {\it Stochastic models for performance analyses
  of iterative algorithms in distributed environments}
  \item[] Advisors: Prof. Jack J. Dongarra and Prof. Michael G. Thomason
  \end{itemize}


\item []{\bf M.S.} -- Dipl\^ome d'\'Etudes Approfondies (DEA) in Parallel
Architectures and Applied Mathematics, National Polytechnic Institute of Toulouse, France, {\bf 1994}.
  \begin{itemize}
  \item[] Thesis: {\it A version of PVM for shared- and virtually shared-memory supercomputers}
  \item[] Advisor: Prof. Michel Dayd\'e
  \end{itemize}

\item []{\bf B.S.} -- Dipl\^ome d'Ing\'enieur in Computer Science
and Applied Mathematics, Ecole Nationale Sup\'erieure d'Electronique,
d'Electrotechnique, d'Informatique et d'Hydraulique de Toulouse (ENSEEIHT), Toulouse, France, {\bf 1993}.
\end{description}

\noindent
{\large{\bf RESEARCH INTERESTS}}

High performance computing, parallel and distributed computing,
parallel application scheduling,
simulation of distributed applications and platforms.

\noindent
{\large{\bf PROFESSIONAL EXPERIENCE}}

\begin{description}
\item [{\bf 07/15 - present:}] Professor, Information and Computer Sciences Department,  University of Hawai`i at M\=anoa.
\item [{\bf 04/12 - 03/18:}] Visiting Professor, National Institute of Informatics,  Tokyo, Japan.
\item [{\bf 07/07 - 06/15:}] Associate Professor, Information and Computer Sciences Department,  University of Hawai`i at M\=anoa.
\item [{\bf 08/05 - 06/07:}] Assistant Professor, Information and Computer Sciences Department,  University of Hawai`i at M\=anoa.
\item [{\bf 07/04 - 07/05:}]  Associate Research Scientist, 
       San Diego Supercomputer Center, University of California, San Diego.
\item [{\bf 07/02 - 07/05:}]  Adjunct Assistant Professor, 
       Department of Computer Science and Engineering, University of California, San Diego.
\item [{\bf 07/01 - 06/04:}]  Assistant Research Scientist, 
       San Diego Supercomputer Center, University of California San Diego.
\item [{\bf 07/01 - 07/05:}]  Director of the Grid Research And Innovation Laboratory (GRAIL), University of California San Diego. 

\item [{\bf 12/98 - 06/01:}] Assistant Project Scientist, Department of
       Computer Science and Engineering, University of California, San Diego.
\item [{\bf 03/98 - 11/98:}] Postdoctoral Research Associate, Computer Science Department, University of Tennessee, Knoxville.
\item [{\bf 01/95 - 02/98:}] Graduate Research Assistant, Computer Science Department, University of Tennessee, Knoxville.
\item [{\bf 11/93 - 11/94}:] Computer Science Advisor, French Ministry of Defense (DGA), Paris, France.
\item [{\bf 09/92 - 10/93}:] Graduate Research Assistant, Computer Science Research Institute of Toulouse (IRIT), Toulouse, France.


\end{description}

\noindent
{\large{\bf PUBLICATIONS}}

\input{publications}

\noindent
{\large{\bf INVITED PRESENTATIONS, TUTORIALS, and COLLOQUIA}}

\begin{itemize}

    \item [-] {\it Checkpointing Workflows for Fail-Stop Failures}, 
Information Science Institute, Los Angeles, California, Nov. 2018.

\item [-] {\it Scheduling and Simulating Parallel and Distributed
Applications}, 6-session seminar series, National Institute for
Informatics, Tokyo, Japan, Oct. 2013.

\item [-] {\it Cost-Optimal Execution of Boolean Query Trees with Shared
Streams}, INRIA Workshop on Scheduling for Exascale Systems, Dagstuhl
Schloss, Germany, Sep. 2013.

\item [-] {\it A Case for Random Topologies in HPC Interconnects},
INRIA Workshop on Scheduling, Pittsburgh, Pennsylvania, 
Jun. 2012.

\item [-] {\it Challenges and Hopes for Scheduling Parallel Applications on Desktop Grids}, {\bf Keynote Address}, Workshop on Desktop Grids and Volunteer Computing Systems (PCGrid'11), Anchorage, Alaska, May 2011. 

\item [-] {\it Flexible Cluster Sharing}, Institut de Recherche
en Informatique de Toulouse, Toulouse, France, Nov. 2008. 

\item [-] {\it Parallel resource sharing: Shortcomings, Cheats, and
Perspectives}, Sept. of Computer Science, University of Bologna, Bologna,
Italy, Jun. 2008.


\item [-] {\it Scheduling Mixed-Parallel Applications with Advance
Reservations}, INRIA Workshop on scheduling for large scale distributed
platforms, Aussois, France, May 2008.

\item [-] {\it Simulation for Large-Scale Distributed Computing Research},
tutorial at the 8th IEEE International Symposium on Cluster Computing and the Grid (CCGrid'08), Lyon, France, May 2008.

\item [-] {\it Grid Computing: Technology and Applications}, invited
plenary presentations at Telecom'05, Hawai`i TeleCommunication Association,
Honolulu, Hawai`i, Oct. 2005.

\item [-] {\it Scheduling and Deploying Applications on Large-Scale
Platforms}, invited lecture at the Departamento de Inform\'atica, Centro
Universitario de M\'erida, M\'erida, Spain, Jun. 2005.

\item [-] {\it Simulation for Grid Computing}, {\bf Keynote Address},
2nd International Grid Performance Workshop, Edinburgh, United Kingdom,
Jun. 2005.

\item [-] {\it Grid Computing: Principles, Software, Applications, and Tools},
{\bf Keynote Address}, 2nd Workshop on New Frontiers of Bioinformatics in Latin America -- Gridding
Biology, Merida, Venezuela, Nov. 2004.

\item [-] {\it Grid platform modeling issues for scheduling research },
Workshop on scheduling for large scale distributed platforms, Aussois,
France, Aug. 2004.

\item [-] {\it Grid Technology, Application, and Research}, presentation 
to the IEEE Society, University of California, La Jolla, California, May 2004.

\item [-] {\it Deploying Applications on the Grid: Engineering and
Research}, University of San Diego, San Diego, California, Sep. 2003.

\item [-] {\it Divisible Workload Scheduling}, Paris XI University,
Orsay, France, Jun. 2003.

\item [-] {\it UMR and RUMR: Algorithms to Schedule Divisible Workloads},
the Tokyo Institute of Technology (TITECH), Tokyo, Japan, 
May 2003.

\item[-] {\it MCell on the Grid: applications, software, research,
and impact}, Plenary presentation at the National Parternship for Advanced
Computing Infrastructure All-Hands Meeting (NPACI-AHM), La Jolla,
California, Mar. 2003.


\item[-] {\it From Parameter Sweep Applications to Divisible Workloads},
Workshop on Distributed Computing, Metacomputing, and Resource
Globalization, Aussois, France, Nov. 2002.

\item[-] {\it An Introduction to Grid Computing}, the Salk Institute,
La Jolla, California, Nov. 2002.

\item[-] {\it Processor Swapping for Enterprise Computing}, Workshop
on Cluster and Computational Grids for Scientific Computing, Faverges,
France, Sep. 2002.

\item[-] {\it Deploying and Scheduling Parameter Sweep Applications},
Entropia Inc., San Diego, California, Mar. 2002.

\item[-] {\it From Grid to Global Computing: Deploying and Scheduling
Parameter Sweep Applications}, Organization for Parallel Computing
Research (ORAP), Saclay, France, Mar. 2002.

\item[-] {\it The Virtual Instrument Project}, National Science Foundation
Workshop on Information Technology Research and Education, Palo Alto,
California, Mar. 2002.

\item[-] {\it APST and its Uses on Clusters}, IEEE Cluster 2001
Conference, Cluster Application Panel, Newport Beach, California,
Oct. 2001.

\item[-] {\it Promoting the Grid with APST}, 1st US/UK Grid Workshop,
San Francisco, California, Aug. 2001.

\item[-] {\it Simulation for Application Scheduling}, Monash University,
Melbourne, Australia, May 2001.

\item[-] {\it The AppLeS Parameter Sweep Template: User-Level Middleware
for the Grid}, NASA IPG workshop, NASA Ames Research Center, Sep.
2000.

\item[-] {\it Internet-wide Scientific Software Access with NetSolve},
{\bf Keynote Address},
Workshop on Internet Accessible Mathematical Computation, Vancouver,
Jul. 1999.

\item[-] {\it Network-enabled Servers}, SIAM Annual Meeting 1999, Atlanta,
May 1999.

\item[-] {\it NetSolve: Current and Future Deployment}, Workshop on
Global and Cluster Computing, Tsukuba, Japan, Mar. 1998.

\item[-] {\it NetSolve: Concepts and Applications}, Danish Computing
Centre for Research and Education, Lungby, Denmark, Dec. 1996.

\item[-] {\it Introduction to the NetSolve Project}, Mathematics and
Computer Science Department of Emory University, Atlanta, Georgia, Oct. 1996.

\end{itemize}

\noindent
{\large{\bf FUNDING AWARDS}}
\begin{itemize}


\item[-] \$500,000 / 3 years (PI), National Science Foundation, 10/19 - 09/22~\\
    {\it Integrating core CI literacy and skills into university curricula via simulation-driven activities}


\item[-] \$500,000 / 3 years (PI), National Science Foundation, 01/17 - 12/20~\\
{\it WRENCH: A Simulation Workbench for Scientific Worflow Users, Developers, and Researchers}

\item[-] \$31,764 / 3 years (co-PI), National Science Foundation, 06/09 - 05/12~\\
{\it DiRT: A Testbed for Distributed Research}

\item[-] \$500,000 / 3 years (co-PI), National Science Foundation, 10/05 - 09/08~\\
{\it Designing Large-Scale Distributed Systems for Realistic Failure Models}

\item[-] \$5,400,000 / 5 years (co-PI), National Science Foundation, 10/03 - 09/08~\\
        {\it Virtual Grid Application Development Software (VGrADS)}

\item[-] \$500,000 / 3 years (PI), National Science Foundation , 07/03 - 06/06~\\
	{\it Models to Support Performance-Engineering of Global Computations}

\item[-] \$48,000 / 3 years (co-PI), National Science Foundation / Institut National de Recherche en Informatique et en Automatique, 07/03 - 06/06~\\
	{\it Algorithms and Simulations for Scheduling on Large-Scale Distributed Platforms}


\item[-] \$450,000 / 3 years (co-PI), National Science Foundation, 01/03 - 12/05~\\
	{\it Autonomous Scheduling on Large Distributed Systems}

\item[-] \$235,000 / 1 year (PI), National Science Foundation, FY 2004~\\
      \emph{National Partnership for Advanced Computational Infrastructure (NPACI)}


\item[-] \$750,000 / 3 years (co-PI), National Science Foundation, 09/02 - 08/05~\\
	{\it Data Intensive Grid Benchmarks}

\item[-] \$792,000 / 3 years (co-PI), National Science Foundation, 10/02 - 09/05~\\  
      {\it Optimizing Performance and Reliability in Distributed Computing Systems 
       Through Wide Spectrum Storage Services}

\item[-] \$270,000 / 1 year (PI), National Science Foundation, FY 2003~\\
      \emph{National Partnership for Advanced Computational Infrastructure (NPACI)}


\item[-] \$700,000 / 2 years (co-PI), National Science Foundation, 07/02 - 06/04~\\
      {\it GridSolve:  A System for Grid-enabling General Purpose Problem Solving Environments}

\item[-] \$280,000 / 1 year (PI), National Science Foundation, FY 2002~\\
      \emph{National Partnership for Advanced Computational Infrastructure (NPACI)}

\item[-] \$2,500,000 / 3 years (co-PI), National Science Foundation, 09/00 - 08/03~\\
{\it Virtual Instruments: Scalable Software Instruments for the Grid}

\item[-] \$1,300,000 / 3 years (co-PI), National Science Foundation, 08/99 - 07/02~\\
{\it Logistical QoS through Application-driven Scheduling of Remote Storage}

\end{itemize}

\noindent
{\large{\bf ADVISING}}


\noindent
{\bf Ph.D. Dissertation Advising and Co-Advising:}
 Benjamin Karsin (2018); 
 Michael Gowanlock (2015);
 Mark Stillwell (2010); 
 Joshua Wingstrom (2009);
 Richard Huang (2007); 
 Derrick Kondo (2005);
 Yang Yang (2005);
 Alan Su (2003);
 Marcio Faerman (2003).

\noindent
{\bf M.S. Thesis Advising and Co-Advising:}
 Evan Hataishi (2019);
 Lambert Leong (2018);
 Suraj Pandey (2018);
 Benjamin Karsin (2012);
 David Schanzenbach (2011);
 Kaveh Kardan (2010);
 Kayo Fujuwara (2007);
 Krijn van der Raadt (2004);
 Charles Wurster (2004);
 Gregory Chun (2003);
 Otto Sievert (2003);
 Nadya Williams (2002);
 Holly Dail (2002);
 Shava Smallen (2001).

\noindent
{\bf Postdoctoral Researcher Advising:}
 Arnaud Legrand (2005);
 Gilles F\'edak (2004);
 Fr\'ed\'eric Suter (2003);
 Yudith Cardinale (2003).


\noindent
{\large{\bf TEACHING}}


\begin{itemize}
\item [-] UHM, ICS312 (UG): Machine-Level and Systems Programming (FA19,  SP19, SP18, SP17, SP16, SP15, SP14, SP10, SP09, FA07)
\item [-] UHM, ICS432 (UG): Concurrent and High-Performance Programming (FA19,  SP17, SP16, SP15, FA11, FA08, SP07, SP06)
\item [-] UHM, ICS632 (GR): Principles of High Performance Computing (FA18, FA17, FA16, FA15, FA14, FA08, FA07, FA06, FA05)
\item [-] UHM, ICS332 (UG): Operating Systems (FA19, SP19, SP18, FA17, SP14, SP13, FA12, SP12, SP11, FA09)
\item [-] UHM, ICS690 (GR): Graduate Seminar (SP13, FA12, SP12, FA11, SP11, FA10, SP10, FA09, SP09)
\item [-] UHM, ICS431 (UG): Computer Architecture (SP08, FA06)
\item [-] UCSD, CSE130 (UG): Programming Languages (SP05, SP04, SP03)
\item [-] UCSD, CSE260 (GR): Parallel Computing (FA04)
\end{itemize}

\noindent
{\large{\bf AWARDS / HONORS}}
\begin{itemize}
\item[-] Chancellor's Citation for Meritorious Teaching, UH M\=anoa, 2018.
\item[-] Visiting Associate Professor, National Informatics Institute (NII), Japan, 2012-2019.
\item[-] Chancellor's Citation for Meritorious Teaching, UH M\=anoa, 2012.
\item[-] Best paper award at HeteroPar, Aug. 2009.
\item[-] Best student paper award at SC, Nov. 2001 (M.S. adviser of Shava Smallen).
\item[-] R\&D 100 Award for designing and developing the NetSolve project, 1999.
\end{itemize}

\noindent
{\large\bf{PROFESSIONAL SERVICES}}

\noindent
{\bf University Services}
\begin{itemize}
\item [--] Fall 2015: Associate Chair of the Information and Computer Sciences Department. 
\item [--] Spring 2009 - Spring 2013: Chair of the Computer Science Graduate Program, University of Hawai`i at M\=anoa.
\end{itemize}

\noindent
{\bf Conference Chairing}

\begin{itemize}
\item [2020]
\item[--] {\bf Algorithm Track Chair}: International Conference on Parallel Processing, Edmonton, Canada, Aug 2020.
\item [2017]
\item[--] {\bf Local Arrangement Co-Chair}: IEEE Cluster Computing Conference, Honolulu, Hawai`i, Sep. 2017. 
\item [2013]
\item[--] {\bf Co-organizer}: INRIA \emph{Workshop on Scheduling Algorithms for Exascale}, Dagstuhl Schloss, Germany, Sep. 2013.
\item[--] {\bf Publicity Chair}: 42nd International Conference on Paralle Processing (ICPP),  Lyon, France, Oct. 2013.
\item [2011]
\item[--] {\bf Program Vice-Chair}: 11th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing (CCGrid), Newport Beach, California, May 2011.
\item [2010]
\item[--] {\bf Program Vice-Chair}: IEEE/ACM Grid Conference, Brussels, Belgium, Oct. 2010.
\item [2009]
\item[--] {\bf Program Co-Chair}: ACM/IEEE International Symposium on High Performance Distributed Computing (HPDC-18), Garching, Germany, Jun. 2009.
\item[--] {\bf Program Vice-Chair}: 9th IEEE Symposium on Cluster Computing and the Grid (CCGrid'09), Shanghai, China, May 2009.
\item [2008]
\item[--] {\bf Program Co-Chair}: 9th IEEE/ACM International Conference on Grid Computing (Grid 2008), Tokyo, Japan, Nov. 2008.
\item[--] {\bf Co-organizer}: NSF/INRIA \emph{Workshop on Scheduling Algorithms for Large-Scale Distributed Platforms}, Aussois, France, May 2008.
\item[--] {\bf Publicity Chair}: 8th IEEE Symposium on Cluster Computing and the Grid (CCGrid'08), Lyon, France, May 2008.
\item[--] {\bf General Chair}: Heterogeneous Computing Workshop (HCW'08), Miami, Florida, Apr. 2008.
\item [2007]
\item[--] {\bf Program Topic Chair}: Euro-Par 2007 (Scheduling and Load Balancing topic), Rennes, France, Aug. 2007.
\item[--] {\bf Program Chair}: Heterogeneous Computing Workshop (HCW'07), Long Beach, California, Mar. 2007.
\item [2005]
\item[--] {\bf Program Vice-Chair}: 6th International Workshop on Grid Computing (Grid'05), Seattle, Washington, Nov. 2005.
\item[--] {\bf Co-organizer}: NSF/INRIA \emph{Workshop on Scheduling Algorithms for Large-Scale Distributed Platforms}, San Diego, California, Nov. 2005.
\item [2004]
\item[--] {\bf General Chair}: \emph{IEEE Conference on Cluster Computing (Cluster'04)}, San Diego, Sep. 2004.
\item[--] {\bf Co-organizer}: NSF/INRIA \emph{Workshop on Scheduling Algorithms for Large-Scale Distributed Platforms}, Aussois, France, Aug. 2004.
\item [2003]
\item[--] {\bf Invited Speaker Chair}: International Conference for High Performance Computing and Communications (SC'03), Phoenix, Arizona, Nov. 2003.
\item [1999]
\item[--] {\bf Organizer}: Mini-symposium on Network-enabled Servers, SIAM Annual Meeting 1999, Atlanta, Georgia, May 1999.
\end{itemize}

\noindent
{\bf Journals}
\begin{itemize}
\item[--] 2012-2016: {\bf Subject Area Editor} for the \emph{Parallel Computing} journal.
\item[--] 2004-2009: Member of the {\bf Editorial Board} of the \emph{Future Generation Computer Systems} journal.
\item[--] 2006: {\bf Guest Editor} for a special issue of the \emph{International Journal of High Performance Computing and Applications}.
\item[--] 2005: {\bf Guest Editor} for the a special issue of the \emph{IEEE Transactions on Parallel and Distributed Systems (TPDS)}. 
\end{itemize}

\noindent
{\bf Conference Program Committees}
\begin{itemize}
\item [2020]
\item[--]  15th Workflows in Support of Large-Scale Science (WORKS) Workshop, Georgia, Atlanta, November 2020.
\item [--] Conf\'rence francophone d'informatique en Parall\'lisme, Architecture et Syst\`me (COMPAS), Lyon, France, June 2020.
\item [--] 34rd IEEE International Parallel and Distributed Processing Symposium (IPDPS), New Orleans, Louisiana, May 2020.
\item [2019]
\item[--]  14th Workflows in Support of Large-Scale Science (WORKS) Workshop, Denver, Colorado, November 2019.
\item[--]  23rd Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP), Rio de Janeiro, Brazil, May 2019.
\item[--]  19th IEEE International Symposium on Cluster, Cloud and Grid Computing (CCGrid), Larnaca, Cyprus, May 2019.
\item[--]  33rd IEEE International Parallel and Distributed Processing Symposium (IPDPS), Rio de Janeiro, Brazil, May 2019.

\item [2018]
\item[--]  13th Workflows in Support of Large-Scale Science (WORKS) Workshop, Dallas, Texas, November 2018.
\item[--]  22nd Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP), Vancouver, Canada, May 2018.
\item[--]  25th IEEE International Conference on. High Performance Computing, Data, and Analytics (HiPC), Bengaluru, India, December 2018.

\item [2017]
\item[--]  12th Workflows in Support of Large-Scale Science (WORKS) Workshop, Denver, Colorado, November 2017.
\item[--]  24th IEEE International Conference on. High Performance Computing, Data, and Analytics (HiPC), Jaipur, India, December 2017.
\item[--]  21st Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP), Orlando, Florida, June 2017.
\item[--]  31st IEEE International Parallel and Distributed Processing Symposium (IPDPS), Orlando, Florida, May 2017.
\item[--]  17th IEEE International Symposium on Cluster, Cloud and Grid Computing (CCGrid), Madrid, Spain, May 2017.

\item [2016]
\item[--]  20th Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP), Hyderabad, Chicago, Illinois, May 2016.
\item[--]  1st Workshop on Fault Tolerance for Extreme Scale Computing, 
Kyoto, Japan, May 2016.
\item[--]  30th IEEE International Parallel and Distributed Processing Symposium (IPDPS), Chicago, Illinois, May 2016.
\item[--] 45th International Conference on Parallel Processing (ICPP),  Philadephia, Pennsylvania, Aug. 2016.

\item [2015]
\item[--]  Workshop on Scheduling for Parallel Computing, Krakow, Poland, Sep. 2015.
\item[--]  EuroPar Conference, Scheduling and Load Balancing track, Vienna, Austria, Aug. 2015.
\item[--]  Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP), Hyderabad, India, May 2015.
\item[--]  29th IEEE International Parallel and Distributed Processing Symposium (IPDPS), Hyderabad, India, May 2015.
\item[--] 44th International Conference on Parallel Processing (ICPP),  Paris, France, Mar. 2015.
\item[--]  9th ACM Richard Tapia Celebration of Diversity in Computing (Tapia2015), Boston, Massachusetts, Feb. 2015.

\item [2014]
\item[--]  Workshop on Reproducible Parallel Computing, Porto, Portugal,
Aug. 2014.
\item[--]  Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP), Phoenix, Arizona, May 2014.
\item[--]  International Conference for High Performance Computing, Networking, Storage, and Analysis (SC), New Orleans, Louisiana, Nov. 2014.

\item [2013]
\item[--] 42nd International Conference on Parallel Processing (ICPP),  Lyon, France, Oct. 2013.
\item[--] 1st conference on Energy Efficiency on Large Scale Distributed Systems (EE-LSDS), Vienna, Austria, Apr. 2013.
\item[--] 17th Workshop on Job Scheduling Strategies for Parallel Processing, Boston, Massachusetts, May 2013.
\item[--] Workshop on Scheduling for Parallel Computing, Warsaw, Poland, Sep. 2013.
\item[--]  13th IEEE International Symposium on Cluster, Cloud and Grid
Computing (CCGrid), Delft, The Netherlands, May 2013.
\item[--]  IEEE Computer Society's Technical Committee on Parallel Processing's Ph.D. Forum at IPDPS, Boston, Massachusetts, May 2013.
\item[--]  27th International Parallel and Distributed Processing Symposium (IPDPS), Boston, Massachusetts , May 2013.
\item[--]  22nd IEEE Symposium on High-Performance Distributed Computing (HPDC-22), New York, New York, Jun. 2013. 

\item [2012]
\item[--]  IEEE Cluster Conference, Beijing, China, Sep. 2012.
\item[--]  3rd Workshop on Scientific Cloud Computing, Delft, The Netherlands, Jun. 2012.
\item[--]  41st  International Conference on Parallel Processing  (ICPP), Pittsburgh, Pensylvania, Sep. 2012.
\item[--]   25th IEEE International Symposium on Computer-Based Medical Systems (CBMS), Rome, Italy, Jun. 2012.
\item[--]  26th International Parallel and Distributed Processing Symposium (IPDPS), Shanghai, China, May 2012.
\item[--]  IEEE Computer Society's Technical Committee on Parallel Processing's Ph.D. Forum at IPDPS, Shanghai, China, May 2012.
\item[--]  12th IEEE International Symposium on Cluster, Cloud and Grid
Computing (CCGrid), Ottawa, Canada, May 2012.
\item[--]  16th Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP),  Shanghai, China, May 2012.

\item [2011]
\item[--]  IEEE Cluster Conference, Austin, Texas, Sep. 2011.
\item[--]  Workshop on Scheduling for Parallel Computing, Torun, Poland, Sep. 2011.
\item[--]  40th International Conference on Parallel Processing (ICPP), Taipei, Taiwan, Sep. 2011.
\item[--]  2nd Workshop on Scientific Cloud Computing (ScienceCloud), San Jose, California, Jun. 2011. 
\item[--]  IEEE Computer Society's Technical Committee on Parallel Processing's Ph.D. Forum at IPDPS, Anchorage, Alaska, May 2011.
\item[--]  5th Workshop on Desktop Grids and Volunteer Computing Systems (PCGrid), Anchorage, Alaska, May 2011.
\item[--]  25th International Parallel and Distributed Processing Symposium (IPDPS), Anchorage, Alaska, May 2011.

\item [2010]
\item[--] 17th IEEE International Conference on High Performance Computing (HiPC), Goa, India, Dec. 2010.
\item[--]  International Conference for High Performance Computing, Networking, Storage, and Analysis (SC), New Orleans, Louisiana, Nov. 2010.
\item[--]  3rd Workshop on Many-Task Computing on Grids and Supercomputers, (MTAGS), New Orleans, Louisiana, Nov. 2010.
\item[--] 4th International Workshop on HealthGrid \& Cloud Computing, Perth, Australia, Oct. 2010.
\item[--]  1st Workshop on Scientific Cloud Computing (ScienceCloud), Chicago, Illinois, Jun. 2010. 
\item[--]  19th IEEE Symposium on High-Performance Distributed Computing (HPDC-19), Chicago, Illinois, Jun. 2010. 
\item[--]  IEEE Computer Society's Technical Committee on Parallel Processing's Ph.D. Forum at IPDPS, Atlanta, Georgia, May 2010.
\item[--]  4th Workshop on Desktop Grids and Volunteer Computing Systems (PCGrid), Melbourne, Australia, May 2010.
\item[--]  10th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing (CCGrid), Melbourne, Australia, May 2010.
\item[--]  15th Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP),  Atlanta, Georgia, Apr. 2010.

\item [2009]
\item[--]  International Conference for High Performance Computing, Networking, Storage, and Analysis (SC), Portland, Oregon, Nov. 2009.
\item[--]  Workshop on Scheduling for Parallel Computing, Krakow, Poland, Sep. 2009.
\item[--]  8th International Symposium on Parallel and Distributed Computing (ISPDC), Lisbon, Portugal, Jun. 2009.
\item[--]  Workshop on Grids, Clouds and Virtualization (WGCV), Geneva, Switzerland, May 2009.
\item[--]  Fourth Workshop on System Management Tools for Large-Scale Parallel Systems (SMTPS), Rome, Italy, May 2009.
\item[--]  8th IEEE International Symposium on Cluster Computing and the Grid (CCGrid), Shanghai, China, May 2009.
\item[--]  3rd Workshop on Desktop Grids and Volunteer Computing Systems (PCGrid), Rome, Italy, May 2009.
\item[--]  IEEE Computer Society's Technical Committee on Parallel Processing's Ph.D. Forum at IPDPS, Rome, Italy, May 2009.
\item[--]  2009 ACM Symposium on Applied Computing (SAC), Honolulu, Hawaii, U.S.A., Mar. 2009.

\item [2008]
\item[--]  High Performance Data Grid (HPDataGrid'08) workshop, Dunedin, New Zealand, Dec. 2008.
\item[--]  1st International Workshop on Robust Scheduling (RobShed'08), Melbourne, Australia, Dec. 2008.
\item[--]  14th IEEE International Conference on Parallel and Distributed Systems (ICPADS'08), Melbourne, Australia, Dec. 2008.
\item[--]  International Symposium on Parallel and Distributed Processing and Applications (ISPA'08), Sydney, Australia, Sep. 2008.
\item[--]  17th IEEE Symposium on High-Performance Distributed Computing (HPDC-17), Boston, Massachusetts, Jun. 2008. 
\item[--]  1st Workshop on Assessing Models of Networks and Distributed Computing Platforms, Lyon, France, May 2008. 
\item[--]  8th IEEE Symposium on Cluster Computing and the Grid (CCGrid'08), Lyon, France, May 2008. 
\item[--]  International Symposium on Parallel Algorithms, Architectures, and Networks (ISPAN), Sidney, Australia, May 2008.
\item[--]  Third Workshop on System Management Tools for Large-Scale Parallel Systems (SMTPS), Miami, Florida, Apr. 2008.
\item[--]  41st Hawai`i International Conference on System Sciences (HICSS), Software Technology Mini-Track on Grid Computing: Adaptive Software, Tools and Applications, O`ahu, Hawaii, Jan. 2008. 

\item [2007]
\item[--]  International Conference on Parallel Processing (ICPP), Xi'an, China, Sep. 2007. 
\item[--]  1st Workshop on Scheduling for Parallel Computing, Gdansk, Poland, Sep. 2007.
\item[--]  16th International Conference on Computer and Networks (ICCCN), O`ahu, Hawai`i, Aug. 2007.
\item[--]  International Conference on Distributed Computing Systems (ICDCS), Toronto, Canada, Jun. 2007.
\item[--]  16th IEEE Symposium on High Performance and Distributed Computing (HPDC-16), Monterey, California, Jun. 2007.
\item[--]  7th workshop on Global and Peer-to-Peer Computing (GP2PC), Rio de Janeiro, Brazil, May 2007. 
\item[--] Proposal Reviewer and Panel Participant, National Science Foundation, Washington D.C., Apr. 2007.
\item[--]  Third Workshop on System Management Tools for Large-Scale Parallel Systems (SMTPS), Long Beach, California, Mar. 2007.

\item [2006]
\item[--]  12th IEEE International Conference on Parallel and Distributed Systems (ICPADS'06), Minneapolis, Minnesota, Jul. 2006.
\item[--]  15th IEEE Symposium on High Performance and Distributed Computing (HPDC-15), Paris, France, Jun. 2006.
\item[--] Proposal Reviewer and Panel Participant, National Science Foundation, Washington D.C., Apr. 2006.
\item[--]  Third High Performance Grid Computing Workshop (HPGCW'06), Rhodes, Greece, Apr. 2006.
\item[--]  Heterogeneous Computing Workshop (HCW'06), Rhodes, Greece, Apr. 2006.
\item[--]  Second Workshop on System Management Tools for Large-Scale Parallel Systems (SMTPS), Rhodes, Greece, Apr. 2006.
\item[--]  5th Workshop on Global and Peer-to-Peer Computing (WGP2PC'06), Singapore, Apr. 2006. 

\item [2005]
\item[--]  International Conference for High Performance Computing and Communications (SC'05), Seattle, Washington, Nov. 2005.
\item[--] Program Committee for the 1st International Workshop on Parallel Bioinspired Algorithms, Oslo, Norway, Jun. 2005
\item[--]  IEEE International Conference on Pervasive Services (ICPS 2005), Santorini, Greece, Jun. 2005.
\item[--]  4th Workshop on Global and Peer-to-Peer Computing (WGP2P'05), Cardiff, U.K., May 2005. 
\item[--]  First Workshop on System Management Tools for Large-Scale Parallel Systems, Denver, Colorado, Apr. 2005.
\item[--]  Heterogeneous Computing Workshop (HCW'05), Denver, Colorado, Apr. 2005.
\item[--]  High Performance Grid Computing Workshop, Denver, Colorado, Apr. 2005.

\item [2004]
\item[--]  International Conference for High Performance Computing and Communications (SC'04), Pittsburgh, Pennsylvania, Nov. 2004.
\item[--]  17th International Conference on Parallel and Distributed Computing Systems (PDCS 2004), San Francisco, California, Sep. 2004. 
\item[--]  13th IEEE Symposium on High Performance and Distributed Computing (HPDC-13), Honolulu, Hawai`i, Jun. 2003.
\item[--]  3rd Workshop on Global and Peer-to-Peer Computing (WGP2P'04), Chicago, Illinois, Apr. 2004. 

\item [2003]
\item[--]  International Conference for High Performance Computing and Communications (SC'03), Phoenix, Arizona, Nov. 2003.
\item[--] Proposal Reviewer and Panelist, National Science Foundation, Washington, DC., Oct. 2003.
\item[--] Program Committee member for Euro-Par 2003, Klagenfurt, Austria, Aug. 2003.
\item[--]  Workshop on Innovative Solutions for Grid Computing (InnoGrid'03), Melbourne, Australia, Jun. 2003. 
\item[--]  12th IEEE Symposium on High Performance and Distributed Computing (HPDC-12), Seattle, Washington, Jun. 2003.
\item[--]  ACM SIGPLAN Symposium on Principles and Practice of Parallel Programming (PPoPP), San Diego, California, Jun. 2003.
\item[--]  3rd IEEE Symposium on Cluster Computing and the Grid (CCGrid'03), Tokyo, Japan, May 2003. 
\item[--]  3rd Workshop on Global and Peer-to-Peer Computing (WGP2P'03), Tokyo, Japan, May 2003. 
\item[--]  International Parallel and Distributed Processing Symposium (IPDPS'03), Nice, France, Apr. 2003.

\item [2002]
\item[--]  3rd International Workshop on Grid Computing (Grid'02), Baltimore, Maryland, Nov. 2002.
\item[--]   International Conference for High Performance Computing and Communications (SC'02), Baltimore, Maryland, Nov. 2002.
\item[--]  11th IEEE Symposium on High Performance and Distributed Computing (HPDC-11), Edinburgh, U.K., Aug. 2002.
\item[--]  2nd Workshop on Global and Peer-to-Peer Computing (WGP2P'02), Berlin, Germany, May 2002. 

\item [2001]
\item[--]  2nd International Workshop on Grid Computing (Grid'01), Denver, Colorado, Nov., 2001.
\item[--]  Metacomputing Systems and Applications Workshop (MSA'01), Valencia, Spain, Sep. 2001.
\item[--]  Euro-Par'01 Conference, Manchester, U.K., Aug. 2001.
\item[--]  High Performance Computing (HPC'01) Conference, Seattle, Washington, Apr. 2001.

\end{itemize}

\end{document}

